S1: Extended Derivations for `A Data Driven Framework for Patient-Specific Neural Field Modelling'

### 2010-06-24 ltx/PLoS/LaTeX_Manuscript.tex
added bits for checking equation length
made comments to paragraph 1 in the dicussion

\documentclass[10pt]{article}

@@

%% ** EDIT HERE **
%% PLEASE INCLUDE ALL MACROS BELOW

%% END MACROS SECTION

@@

   	\caption{{\bf Example of a field decomposition.} An example of a continuous one-dimensional field decomposed by a finite number of basis functions scaled by the state vector. The dashed line depicts the field and the solid lines show the Gaussian basis functions.} 

@@

The spatial frequency of the observed field is shown in Figure~\ref{fig:ObservationFreqAnal}(C). The cut-off frequency is $\nu_{cy} \approx 0.2$~Hz ($-3$~dB point). The observation cut-off frequency is lower than the field cut-off due to the low-pass filtering effect of the sensors. The spatial frequency response of the sensors can be seen in Figure~\ref{fig:ObservationFreqAnal}(A). Using an oversampling parameter of $\rho_{\phi}=1$, the minimum distance between the field basis functions was calculated to be $2.5$~mm to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}). The distance between basis functions was set to $\Delta_{\phi}=2.5$~mm, which is sufficient to capture the significant dynamics according to our criteria.
Given the basis function separation, the basis function width parameter was set to $\sigma_{\phi}^2=2.5$~mm. This allowed a smooth representation of the field by the basis function decomposition up to a spatial frequency $\mathbf{\nu_{c\phi}} \approx 0.12$~Hz, as described by equation~\ref{eq:CutoffFromBasisFuncWidth}. The band-limiting effect is due to the spatial frequency response of the basis functions as seen in Figure~\ref{fig:ObservationFreqAnal}(B). The spatial frequency of the reconstructed field from the basis function decomposition is shown in Figure~\ref{fig:FFTTrueEstimate}(B). This figure illustrates the band-limiting effect of the basis function decomposition.
\begin{figure}[!ht] 
	\begin{center}
		\includegraphics{./Graph/SensorBasisObsFrequencyResponse.pdf}	
	\end{center}
	\caption{{\bf Spatial frequency analysis}. The dashed line shows the cut-off frequency (-3 dB point). (\textbf{A}) Two-dimensional spatial frequency in power dB, averaged over 400 time steps) of the observed field. The symmetry of the sensors and field basis functions allow for the one-dimensional representation of the spectral characteristics. (\textbf{B}) The spatial frequency response of a one-dimensional model sensor. (\textbf{C}) The spatial frequency response of a one-dimensional neural field basis function, illustrating a narrower band width than the sensors.} 
	\label{fig:ObservationFreqAnal}
\end{figure}

@@

\begin{figure}
\centering 
\label{fig:TrueField}\includegraphics{./Graph/FieldTrueEstimationError.pdf}
\caption{{\bf Examples of the actual and estimated neural fields and the error}. (\textbf{A}) The actual field at a single time instant from the full neural field model that was used to generate data. (\textbf{B}) The reconstructed field of the reduced model, showing the effect of the basis function decomposition on the frequency content of the estimated field. (\textbf{C}) The absolute error between the true and reconstructed fields. The error shows high frequency behaviour.}
\label{fig:FieldEstimate}
\end{figure}

@@

>>>>

% TO DELETE
\newcommand{\mike}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}}

%  \documentclass[twocolumn,10pt]{article}						%<-use this for checking equation length
 \documentclass[10pt]{article}

@@

%% ** EDIT HERE **
%% PLEASE INCLUDE ALL MACROS BELOW
% \usepackage{anysize} 									%<-use this for checking equation length
% \marginsize {1.7cm}{1.5cm}{0.3cm}{0.8cm} 				%<-use this for checking equation length
% \setlength{\columnsep}{0.5cm}							%<-use this for checking equation length
%% END MACROS SECTION

@@

   	\caption{{\bf Example of a field decomposition.} An example of a continuous one-dimensional field decomposed by a finite number of basis functions scaled by the state vector. The dashed line depicts the field and the solid lines shows the Gaussian basis functions.} 

@@

The spatial frequency of the observed field is shown in Figure~\ref{fig:ObservationFreqAnal}(C). The cut-off frequency is $\nu_{cy} \approx 0.2$~Hz ($-3$~dB point). The observation cut-off frequency is lower than the field cut-off due to the low-pass filtering effect of the sensors. The spatial frequency response of the sensors can be seen in Figure~\ref{fig:ObservationFreqAnal}(A). Using an oversampling parameter of $\rho_{\phi}=1$, the minimum distance between the field basis functions was calculated to be $2.5$~mm to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}). The distance between basis functions was set to $\Delta_{\phi}=2.5$~mm, which is sufficient to capture the significant dynamics according to our criteria.
Given the basis function separation, the basis function width parameter was set to $\sigma_{\phi}^2=2.5$~mm. This allowed a smooth representation of the field by the basis function decomposition up to a spatial frequency $\mathbf{\nu_{c\phi}} \approx 0.12$~Hz, as described by equation~\ref{eq:CutoffFromBasisFuncWidth}. The band-limiting effect is due to the spatial frequency response of the basis functions as seen in Figure~\ref{fig:ObservationFreqAnal}(B). The spatial frequency of the reconstructed field from the basis function decomposition is shown in Figure~\ref{fig:FFTTrueEstimate}(B). This figure illustrates the band-limiting effect of the basis function decomposition.
\begin{figure*}[!ht] 
	\begin{center}
		\includegraphics{./Graph/SensorBasisObsFrequencyResponse.pdf}	
	\end{center}
	\caption{{\bf Spatial frequency analysis}. The dashed line shows the cut-off frequency (-3 dB point). (\textbf{A}) Two-dimensional spatial frequency in power dB, averaged over 400 time steps) of the observed field. The symmetry of the sensors and field basis functions allow for the one-dimensional representation of the spectral characteristics. (\textbf{B}) The spatial frequency response of a one-dimensional model sensor. (\textbf{C}) The spatial frequency response of a one-dimensional neural field basis function, illustrating a narrower band width than the sensors.} 
	\label{fig:ObservationFreqAnal}
\end{figure*}

@@

\begin{figure*}
\centering 
\label{fig:TrueField}\includegraphics{./Graph/FieldTrueEstimationError.pdf}
\caption{{\bf Examples of the actual and estimated neural fields and the error}. (\textbf{A}) The actual field at a single time instant from the full neural field model that was used to generate data. (\textbf{B}) The reconstructed field of the reduced model, showing the effect of the basis function decomposition on the frequency content of the estimated field. (\textbf{C}) The absolute error between the true and reconstructed fields. The error shows high frequency behaviour.}
\label{fig:FieldEstimate}
\end{figure*}

@@

\mike{The previous paragraph seems to say this: we get good estimates, but with wide variance. We could shrink those aspects of the variance to do with observation noise by including an input. Then, in a practical setting, do multiple runs to get a distribution of parameters. It seems to me there are two messages here. 1: we could reduce the variance using an input. 2: we could deal with the fact that we get a wide range of parameter estimates in practice by conducting multiple trials. I think these messages could be made a bit more clearly, and turned on their heads a bit. I've had a go at this paragraph again.}

\mike{This paper has presented a method for estimating intracortical connectivity and synaptic dynamics from electrophysiological data. As seen in  Section~\ref{sec:state_and_param_results}, the results indicate ubiased estimation, where the mean parameter estimates are in good agreement with the actual values. The estimates of the connectivity kernel parameters show relatively broad distributions, which can be expected considering the system's input is modelled as a random disturbance, and the observations are corrupted by noise.}

\mike{To overcome the effect of noise, an evoked-response paradigm should be considered when applying the estimation algorithm to electrophysiological recordings. Given knowledge of the input, it is expected that the variance of the parameter estimates will decrease.}

\mike{Even with an evoked potential, our results imply that we should only expect to learn distributions of parameters, rather than hope to uncover a `true' parameter set. By designing an input signal carefully, data could be epoched into a sufficient number of trials (realisations), where each trial is a response to a stimulus, such that a distribution of the parameter estimates can be formed.}
